---
title: "Simple document"
author: Dylan Morgan
date: 2024-09-12
output: 
  html_document:
    toc: true
    toc_float: true
---

```{r, echo = FALSE, message = FALSE}
library(tidyverse)
```
I loaded necessary packages (e.g., `tidyverse`)

I'm an R Markdown document! 

# Section 1

Here's a **code chunk** that samples from 
a _normal distribution_:

```{r}
# you can also do r eval = FALSE within {}
samp = rnorm(100)
length(samp)
```

# Section 2

I can take the mean of the sample, too!
The mean is `r mean(samp)`.


# Learning assessment
This is code for learning assessment at P8105. It creates `la_df` and then plots a histogram.

```{r la_chunk}
### fyi: option + command + I -- creates new code chunk (on Mac)

# create dataframe with: 
## 1. numeric variable containing random sample size 500 from normal variable with mean 1
## 2. logical vector showing whether each sampled value is > 0
## 3. numeric vector containing absolute value of each element

la_df <- 
  tibble(
    norm_samp <- rnorm(n = 500, mean = 1), 
    samp_g0 <- norm_samp > 0, 
    abs_v_samp = abs(norm_samp)
  )

ggplot(la_df, aes(x = abs_v_samp)) + 
  geom_histogram()

```

# Formatting text
Text formatting 
------------------------------------------------------------

*italic*  or  _italic_
**bold**  or  __bold__
`code`
superscript^2^ and subscript~2~


Headings
------------------------------------------------------------

# 1st Level Header

## 2nd Level Header

### 3rd Level Header


Lists
------------------------------------------------------------

*   Bulleted list item 1

*   Item 2

    * Item 2a

    * Item 2b

1.  Numbered list item 1

1.  Item 2. The numbers are incremented automatically in the output.


Tables 
------------------------------------------------------------

First Header  | Second Header
------------- | -------------
Content Cell  | Content Cell
Content Cell  | Content Cell

